SunPy - Python for Solar Physics

### 2014-01-20 4-Util.tex

\subsubsection{constants}
The purpose of the constants package is to provide a number of solar-related constants 
in order to provide consistency in the calculations of derived solar values both within the
SunPy code base but also to the user. Every solar constants is provided as a Constant objects as defined by Astropy. 
Each Constant object defines a Quantity, a number associated with a unit, along with the constant's provenance
(i.e. reference) as well as its uncertainty. Using Astropy's Quantities, any solar constant
can easily be converted between different units as can be seen in Figure~\ref{fig:constants_code} as well
as between SI or cgs with a single command.  As these objects inherit from Numpy's ndarray,
they work well with standard representations of numbers.
For convenience a number shortcuts to frequently used constants are provided directly when importing
the module. A larger list of constants can be accessed through an interface modelled 
on that provided by the SciPy constants package. To view all of the available constants
a print_all() function can be used.

>>>>

\subsubsection{constants}
The purpose of the constants package is to provide a number of solar-related constants 
in order to provide consistency in the calculations of derived solar values both within the
SunPy code base but also to the user. Every solar constants is provided as a Constant objects as defined by Astropy. 
Each Constant object defines a Quantity, a number associated with a unit, along with the constant's provenance
(i.e. reference) as well as its uncertainty. Using Astropy's Quantities, any solar constant
can easily be converted between different units as can be seen in Figure~\ref{fig:constants_code} as well
as between SI or cgs with a single command.  As these objects inherit from Numpy's ndarray,
they work well with standard representations of numbers.
For convenience a number shortcuts to frequently used constants are provided directly when importing
the sub-package. A larger list of constants can be accessed through an interface modelled 
on that provided by the SciPy constants package and are available as a dictionary called
physical_constants. To view all quickly a print_all() function is available.

\begin{listing}[h]
\begin{minted}{pycon}

>>> from sunpy.sun import constants as sun
>>> print(sun.mass)
  Name   = Solar mass
  Value  = 1.9891e+30
  Error  = 5e+25
  Units  = kg
  Reference = Allen's Astrophysical Quantities 4th Ed.
Verify the average density of the Sun and convert to cgs
>>> (sun.mass/sun.volume).cgs
<Quantity 1.40851154227 g / (cm3)>
Check to see if the age of the Sun is available and grab the unit and value separately
>>> sun.find('age')
['age', 'average angular size', 'average density', 'average intensity']
>>> sun.value('age'), sun.unit('age')

\end{minted}
\caption{Using sunpy.sun.constants sub-package.}
\label{code:constants_code}
\end{listing}
